State of the Practice for Lattice Boltzmann Method Software

### 2022-04-26 StateOfPractice/Papers/LatticeBoltz_SOP-arXiv/LatticeBoltz_SOP.tex
Revisions to Section 11.

\subsection{Surface Robustness}

@@

Our threats to validity categories come from an analysis of software engineering
secondary studies by \citet{AmpatzoglouEtAl2019}.  We use the classification of
\citet{AmpatzoglouEtAl2019} because studying a collection of software is a form
of secondary study, where a secondary study analyzes the data from a set of
primary studies.  A common example of a secondary study is a systematic
literature review.  Our methodology is essentially a systematic software review
--- the primary studies are the software, and our work collects and analyzes
these primary studies.

@@

A study is reliable if its data and analysis are independent of the specific
researcher(s) doing the study.  That is, repetition of the study by a different
researcher should achieve the same results, as long as they use the same
methodology \citep{AmpatzoglouEtAl2019}.  For our study the identified
reliability related threats include the following:

@@

Construct validity means that adopted metrics represent what they are intended
to measure \citep{AmpatzoglouEtAl2019}. The construct validity related threats
for the LBM study include the following:

\begin{itemize}
\item Our approximation of popularity by stars and watches
(Section~\ref{repmetrics}) may not be valid. 
\item Our overall AHP ranking makes the unrealistic assumption of equal
weighting between qualities (Section~\ref{Sec_OverallQuality}).
\item The measure of surface robustness in only based on two pieces of data per
project. The measurement of robustness could be expanded, as it currently only
measures the impact of unexpected input. Other intentional faults could be
introduced, but this would require a larger investment of measurement time. 
\item Reusability (Section~\ref{reusabilityresults}) is assessed via the number
of code files and LOC per file. While this measure is indicative of modularity,
it is possible that some packages have many files, with few LOC, but the files
do not contain source code that is easily reusable. The formatting may be poor,
or the source code may be vague and have ambiguous identifiers. 
\item We may have inaccurately estimated maintainability by assuming a higher
ratio of comments to source code improves maintainability
(Section~\ref{Sec_Maintainability}). 
\item The measurement of understandability
(Section~\ref{Sec_SurfUnderstandability}) relies on 10 random source code files.
By random chance, the 10 files that were chosen may not be representative. 
\item We measure our software qualities indirectly, rather than directly.
Unfortunately meaningful direct measures for qualities like maintainability,
reusability and verifiability, are not available.  Therefore, we follow the
usual approach of assuming that following procedures and adhering to standards
yields a higher-quality product \citep[p.\ 112]{VanVliet2000}.
\end{itemize}

@@

A study is internally valid if the discovered causal relations are trustworthy
and cannot be explained by other factors \citep{AmpatzoglouEtAl2019}. The
internal validity threats include the following:

\begin{itemize}
\item We may have missed a relevant software package in our search for LBM
software packages (Section~\ref{identifysoftware}).
\item A temporal gap exists between the manual measurement of Musubi and the
measurement of all other packages (Section~\ref{identifysoftware}). This gap
caused a mismatch between the time of manual and automated data collection
(Section~\ref{repmetrics}), since we updated the automated measures (like the
number of files, LOC, etc.) when Musubi was added.
\item Our interviews were with a relatively small sample of four LBM developers.
The pain points they expressed may not be representative of others in the
community.
\item In our manual measures of the software repositories, we may have missed
some data due to technology issues like broken links. This issue arose with the
measurement of Palabos, which had a broken link to its user manual, as noted in
Section~\ref{Sec_CompareArtifacts}. 
\item Our methodology assumes that artifacts will be present in the repositories
to show the approach used for software development.  However, not all activities
will necessarily leave a trace in the repositories. For instance, only three
packages (ESPResSo, Ludwig, Musubi) show evidence in their artifacts of unit
testing and CI (Section~\ref{SecSurfCorrectAndVerifiab}), even though interviews
suggest a more frequent use of both unit testing and CI. For example, OpenLB,
pyLBM, and TCLB use such methods during development despite this not being
explicit from an analysis of the material available online.
\end{itemize}

@@

External validity concerns whether the results of the study can be generalized
(applied) to other situations/cases \citep{AmpatzoglouEtAl2019}.  The scope of
our work is LBM solvers.  We are confident that our search was exhaustive and
that we did not miss any highly popular examples.  Therefore, our validity
concerns about LBM software observations are internal
(Section~\ref{Sec_InternalValidity}), not external.  However, our hope is that
the trends observed, and the lessons learned for LBM software can be applied to
other research software.  With that in mind we identified the following threat
to external validity:

\begin{itemize}
\item The development of LBM software is fundamentally different from other
research software.
\end{itemize}

>>>>

\subsection{Surface Robustness} \label{Sec_Robustness}

@@

Our categories for threats to validity come from an analysis of software
engineering secondary studies by \citet{AmpatzoglouEtAl2019}, where a secondary
study analyzes the data from a set of primary studies.  We use the
classification of \citet{AmpatzoglouEtAl2019} because a common example of a
secondary study is a systematic literature review. Our methodology is
essentially a systematic software review --- the primary studies are the
software packages, and our work collects and analyzes these primary studies.

@@

A study is reliable if its data and analysis are independent of the specific
researcher(s) doing the study.  That is, repetition of the study by a different
researcher should achieve the same results, as long as they use the same
methodology \citep{RunesonAndHost2009}.  For our study the identified
reliability related threats include the following:

@@

Construct validity means that adopted metrics represent what they are intended
to measure \citep{RunesonAndHost2009}. The construct validity related threats
for the LBM study include the following:

\begin{itemize}
\item We measure our software qualities indirectly, rather than directly.
Unfortunately meaningful direct measures for qualities like maintainability,
reusability and verifiability, are not available.  Therefore, we follow the
usual approach of assuming that following procedures and adhering to standards
yields a higher-quality product \citep[p.\ 112]{VanVliet2000}.
\item The measure of surface robustness (Section~\ref{Sec_Robustness}) is only
based on two pieces of data per project. The measurement of robustness could be
expanded, as it currently only measures the impact of unexpected input. Other
intentional faults could be introduced, but this would require a larger
investment of measurement time. 
\item We may have inaccurately estimated maintainability by assuming a higher
ratio of comments to source code improves maintainability
(Section~\ref{Sec_Maintainability}). 
\item Reusability (Section~\ref{reusabilityresults}) is assessed via the number
of code files and LOC per file. While this measure is indicative of modularity,
it is possible that some packages have many files, with few LOC, but the files
do not contain source code that is easily reusable. The formatting may be poor,
or the source code may be vague and have ambiguous identifiers. 
\item The measurement of understandability
(Section~\ref{Sec_SurfUnderstandability}) relies on 10 random source code files.
By random chance, the 10 files that were chosen may not be representative. 
\item Our overall AHP ranking makes the unrealistic assumption of equal
weighting between qualities (Section~\ref{Sec_OverallQuality}).
\item Our approximation of popularity by stars and watches
(Section~\ref{repmetrics}) may not be valid. 
\end{itemize}

@@

A study is internally valid if the discovered causal relations are trustworthy
and cannot be explained by other factors \citep{RunesonAndHost2009}. The
internal validity threats include the following:

\begin{itemize}
\item We may have missed a relevant software package in our search for LBM
software packages (Section~\ref{identifysoftware}).
\item A temporal gap exists between the manual measurement of Musubi and the
measurement of all other packages (Section~\ref{filtersoftware}). This gap
caused a mismatch between the time of manual and automated data collection,
since we updated the automated measures (like the number of files, LOC, etc.)
when Musubi was added.
\item Our methodology assumes that artifacts in the repositories will show us
the approach used for software development.  However, not all activities will
necessarily leave a trace in the repositories. For instance, only three packages
(ESPResSo, Ludwig, Musubi) show evidence in their artifacts of unit testing and
CI (Section~\ref{SecSurfCorrectAndVerifiab}), even though interviews suggest a
more frequent use of both unit testing and CI. For example, OpenLB, pyLBM, and
TCLB use such methods during development despite this not being obvious from an
analysis of the online material.
\item In our manual measures of the software repositories, we may have missed
some data due to technology issues like broken links. This issue arose with the
measurement of Palabos, which had a broken link to its user manual, as noted in
Section~\ref{Sec_CompareArtifacts}. 
\item Our interviews were with a relatively small sample of four LBM developers.
The pain points (Section~\ref{painpoints}) they expressed may not be
representative of the rest of their community.
\end{itemize}

@@

External validity concerns whether the results of the study can be generalized
(applied) to other situations/cases \citep{RunesonAndHost2009}.  The scope of
our work is LBM solvers.  We are confident that our search was exhaustive and
that we did not miss any highly popular examples.  Therefore, the bulk of our
validity concerns about LBM software observations are internal
(Section~\ref{Sec_InternalValidity}), not external.  However, our hope is that
the trends observed, and the lessons learned for LBM software can be applied to
other research software.  With that in mind we identified the following threat
to external validity:

\begin{itemize}
\item Generalization of our results will not be possible if the development of
LBM software is fundamentally different from other research software.
\end{itemize}
